\addcontentsline{toc}{chapter}{Tài liệu tham khảo}
\begin{thebibliography}{99}

\bibitem{ren2020balanced}
J. Ren, C. Yu, S. Sheng, X. Ma, H. Zhao, S. Yi, and H. Li.
\textit{Balanced Meta-Softmax for Long-Tailed Visual Recognition}.
NeurIPS, 2020.

\bibitem{kang2020decoupling}
B. Kang, S. Xie, M. Rohrbach, Z. Yan, A. Gordo, J. Feng, and Y. Kalantidis.
\textit{Decoupling Representation and Classifier for Long-Tailed Recognition}.
ICLR, 2020.

\bibitem{khosla2020supcon}
P. Khosla, P. Teterwak, C. Wang, A. Sarna, Y. Tian, P. Isola, A. Maschinot, C. Liu, and D. Krishnan.
\textit{Supervised Contrastive Learning}.
NeurIPS, 2020.

\bibitem{snell2017protonet}
J. Snell, K. Swersky, and R. Zemel.
\textit{Prototypical Networks for Few-shot Learning}.
NeurIPS, 2017.

\bibitem{zhang2018mixup}
H. Zhang, M. Cisse, Y. N. Dauphin, and D. Lopez-Paz.
\textit{mixup: Beyond Empirical Risk Minimization}.
ICLR, 2018.

\bibitem{yun2019cutmix}
S. Yun, D. Han, S. J. Oh, S. Chun, J. Choe, and Y. Yoo.
\textit{CutMix: Regularization Strategy to Train Strong Classifiers with Localizable Features}.
ICCV, 2019.

\bibitem{park2022cmo}
S. Park, Y. Hong, B. Heo, S. Yun, and J. Y. Choi.
\textit{The Majority Can Help the Minority: Context-rich Minority Oversampling for Long-tailed Classification}.
CVPR, 2022.

\bibitem{radford2021clip}
A. Radford, J. W. Kim, C. Hallacy, et al.
\textit{Learning Transferable Visual Models From Natural Language Supervision (CLIP)}.
ICML, 2021.

\bibitem{zhang2022tip}
R. Zhang, W. Zhang, R. Fang, P. Gao, K. Li, J. Dai, Y. Qiao, and H. Li.
\textit{Tip-Adapter: Training-free Adaption of CLIP for Few-shot Classification}.
ECCV, 2022.

\bibitem{shi2024lift}
J. Shi, et al.
\textit{Long-Tail Learning with Foundation Model: Heavy Fine-Tuning Hurts (LIFT)}.
ICML, 2024.

\bibitem{pratt2023cupl}
S. Pratt, I. Covert, R. Liu, and A. Farhadi.
\textit{What does a platypus look like? Generating customized prompts for zero-shot image classification (CuPL)}.
ICCV, 2023.

\bibitem{oquab2023dinov2}
M. Oquab, T. Darcet, T. Moutakanni, et al.
\textit{DINOv2: Learning Robust Visual Features without Supervision}.
TMLR, 2023.

\bibitem{han2024ldmlr}
B. Han, et al.
\textit{Latent-based Diffusion Model for Long-tailed Recognition (LDMLR)}.
2024.

\bibitem{zhu2023gla}
B. Zhu, K. Tang, Q. Sun, and H. Zhang.
\textit{Generalized Logit Adjustment: Calibrating Fine-tuned Models by Removing Label Bias in Foundation Models}.
NeurIPS, 2023.

\bibitem{caruana2004ensemble}
R. Caruana, A. Niculescu-Mizil, G. Crew, and A. Ksikes.
\textit{Ensemble Selection from Libraries of Models}.
ICML, 2004.

\bibitem{wortsman2022soups}
M. Wortsman, G. Ilharco, S. Y. Gadre, et al.
\textit{Model Soups: Averaging Weights of Multiple Fine-tuned Models Improves Accuracy without Increasing Inference Time}.
ICML, 2022.

\bibitem{he2016resnet}
K. He, X. Zhang, S. Ren, and J. Sun.
\textit{Deep Residual Learning for Image Recognition}.
CVPR, 2016.

\bibitem{ho2020ddpm}
J. Ho, A. Jain, and P. Abbeel.
\textit{Denoising Diffusion Probabilistic Models}.
NeurIPS, 2020.

\bibitem{wah2011cub}
C. Wah, S. Branson, P. Welinder, P. Perona, and S. Belongie.
\textit{The Caltech-UCSD Birds-200-2011 Dataset}.
Technical Report CNS-TR-2011-001, Caltech, 2011.

\bibitem{krizhevsky2009cifar}
A. Krizhevsky.
\textit{Learning Multiple Layers of Features from Tiny Images (CIFAR)}.
Technical Report, University of Toronto, 2009.

\end{thebibliography}
